A Novel Sampling Method Using Stochastic Gradient Descent

### 2016-12-07 paper/main.tex
Updates from ShareLaTeX

\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case2_l1.pdf}\\
\includegraphics[width=.3\textwidth]{../figure/sim3/case3_l1.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case4_l1.pdf}
\caption{$d(k)$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right). It can be seen that $d(k)$ decreases exponentially for all of the functions. And the mixing time decreases as the degree increases.}\label{Fig:sim3_1}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case2_pdf.pdf}\\
\includegraphics[width=.3\textwidth]{../figure/sim3/case3_pdf.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case4_pdf.pdf}
\caption{Empirical density of $x^k$ for $k = 100$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right). For $\exp(-|x|)$, it has not converge to the true pdf yet. For $\exp(-|x|^4)$, it has already converged.}\label{Fig:sim3_2}
\end{figure}
As shown in Figure \ref{Fig:sim3_1} and Figure \ref{Fig:sim3_2}, the mixing time of $\exp(-|x|)$ is the longest (> 100) and the mixing time of $\exp(-|x|^4)$ is the shortest. This is coherent with their convergence time. For $\exp(-|x|)$, the convergence time is the longest; for $\exp(-|x|^4)$, the convergence time is the longest.
\begin{figure}
\centering
\includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf1.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf2.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf3.pdf}
\caption{Empirical density of $x^k$ for $k = 100, 1000, 10000$ for $\exp(- (x^2 - 1)(x^2 - 4))$. }\label{Fig:sim3_3}
\end{figure}

>>>>

\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case2_l1.pdf}\\
\includegraphics[width=.3\textwidth]{../figure/sim3/case3_l1.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case4_l1.pdf}
\caption{$d(k)$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right). It can be seen that $d(k)$ decreases exponentially for all of the functions. And the mixing time decreases as the degree increases.}\label{Fig:sim3_1}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case2_pdf.pdf}\\
\includegraphics[width=.3\textwidth]{../figure/sim3/case3_pdf.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case4_pdf.pdf}
\caption{Empirical density of $x^k$ for $k = 200$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right). For $\exp(-|x|)$, it has not converge to the true pdf yet. For $\exp(-|x|^4)$, it has already converged.}\label{Fig:sim3_2}
\end{figure}
As shown in Figure \ref{Fig:sim3_1} and Figure \ref{Fig:sim3_2}, the mixing time of $\exp(-|x|)$ is the longest (> 100) and the mixing time of $\exp(-|x|^4)$ is the shortest. This is coherent with their convergence time. For $\exp(-|x|)$, the convergence time is the longest; for $\exp(-|x|^4)$, the convergence time is the longest.
\begin{figure}
\centering
\includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf1.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf2.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf3.pdf}
\caption{Empirical density of $x^k$ for $k = 100, 1000, 10000$ for $\exp(- (x^2 - 1)(x^2 - 4))$. }\label{Fig:sim3_3}
\end{figure}
